Towards a standardized evaluation of multiple imputation routines

### 2022-01-25 Manuscript/StandardizedEvaluation.Rmd
Add script for the small simulation from the manuscript

- add ADEMP paper [@morr18], diagnostic checking paper [@zhao22]
- add PPC (refer to Mingyang, and Gelman & King)
- expand convergence section
- add RMSE
- add insights from literature review for chapter on missing data in EHR

>>>>

- add ADEMP paper [@morr18], diagnostic checking paper [@zhao22]
- add PPC (refer to Mingyang, and Gelman & King)
- expand convergence section
- add RMSE
- add insights from literature review for chapter on missing data in EHR
- add link to simulation script, and $n$
- add simulation results
